Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-02-03 ms.tex
added figure showing best-fit map of f_1 parameter

\subsection{Low Resolution Fits}
%mention that the pixelization changes ---> to lower HEALpix nside
%mention that over some region of the sky with high signal and high
%S/N we try fitting t2, normalization and one of q1/q2, f_1
%using more bands (including 143, and maybe 100 GHz)

@@

\subsection{$T_{2}$ Prior}
Use FIRAS data to justify $T_2$ prior.

@@

>>>>

\subsection{Low-resolution Fits}
%mention that the pixelization changes ---> to lower HEALpix nside
%mention that over some region of the sky with high signal and high
%S/N we try fitting t2, normalization and one of q1/q2, f_1
%using more bands (including 143, and maybe 100 GHz)

As mentioned previously, our baseline fits fix several parameters which
in principle could vary spatially. If we are willing to sacrifice angular
resolution in order to incorporate lower-frequency \PLANCK~bands and
enhance signal to noise, we can introduce additional free parameters
and run the Markov chains in higher dimensions.

We ran the Markov chains in three dimensions by allowing 
$f_1$ to be a third free parameter. We added to our standard posterior a 
term involving.

@@

\subsection{$T_{2}$ Prior}
Use FIRAS data to justify $T_2$ prior. Could I use the DIRBE 100/240 micron
ratio to get a $1.3^{\circ}$ resolution prior on $T_2$?

@@

\begin{figure}
\begin{center}
\epsfig{file=f1_1deg.eps, width=3.3in}
\caption{\label{fig:f1} The results of our low-resolution fit with $f_1$
allowed to vary, but with a strong prior 
$P(f_1)=\mathcal{N}(f_1|0.0363, 0.003)$.}
\end{center}
\end{figure}
